Stack Safety is a Security Property

### 2021-04-16 tex/main.tex
Here's the payoff

\definition
Let \(\mpcstatename\) and \(\mpcstatename'\) be reachable states such that
\(\mpcstatename \stepstocon \mpcstatename'\), and \(\pi_\context(\mpcstatename) = \domMap,\rts\).
A system enjoys {\em stepwise stack integrity with passing} if for all
such states, \(\pi_\mach(\mpcstatename) ~ \component = \pi_\mach(\mpcstatename') ~ \component\)
for each component in \(\mathit{protected}(\pi_\context(\mpcstatename))\)

>>>>

\definition
For each of the stepwise, deferred, and observational versions of
stack integrity in the simple model, the equivalent property in the
passing model substitutes the above definitions of \(\context\), initial contexts and update
function, and \(\mathit{protected}\), and is otherwise identical.
